Meeting Agenda with Domain Experts

### 2021-01-04 StateOfPractice/Methodology/Meeting Agenda with Domain Experts.tex
Deleted tasks asking for feedbacks in Sections 1.2, 1.3, 1.4, 2.1, 2.2, 2.4

In the interest of time, some topics will only be discussed briefly during this
meeting, and tasks will be assigned to domain experts to finish later. For
example, Task \ref{task_overall_objective} in Section \ref{project_objectives}.

@@

Do you have any suggestions? Feedback can be provided later in Task
\ref{task_overall_objective}.

@@

Do you have any suggestions? Feedback can be provided later in Task
\ref{task_research_proposal}.

@@

Do you have any suggestions? Feedback can be provided later in Task
\ref{task_research_questions}.

@@

Do you have any suggestions? Feedback can be provided later in Task
\ref{task_measurement_template}.

@@

Do you have any suggestions? Feedback can be provided later in Task
\ref{task_survey_short_list_projects}

@@

Do you have any suggestions? Feedback can be provided later in Task
\ref{modifiability_experiment}

@@

\subsection{Review the Overall Objective}
\label{task_overall_objective}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{project_objectives}

\subsection{Review the Research Proposal}
\label{task_research_proposal}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{research_proposal}

\subsection{Review the Research Questions}
\label{task_research_questions}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{research_questions}

\subsection{Review the Measurement Template}
\label{task_measurement_template}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{measurement_template}

\subsection{Review the Survey for Short List Projects}
\label{task_survey_short_list_projects}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{survey_short_list_projects}

@@

\subsection{Review the Modifiability Experiment}
\label{task_modifiability_experiment}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\noindent Refer to Section \ref{modifiability_experiment}

>>>>

In the interest of time, some topics will only be discussed briefly during this
meeting, and tasks will be assigned to domain experts to finish later. For
example, Task \ref{task_usability_tests} in Section \ref{usability_tests}.

@@

@@

@@

@@

@@

@@

@@

@@
